---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {catalog}

[![CRAN status](https://www.r-pkg.org/badges/version/catalog)](https://cran.r-project.org/package=catalog)
[![Dependencies](https://tinyverse.netlify.com/badge/catalog)](https://cran.r-project.org/package=catalog)
![CRAN downloads](https://cranlogs.r-pkg.org/badges/catalog)

## Overview

{catalog} gives the user access to the Spark [Catalog](https://spark.apache.org/docs/2.4.3/api/java/org/apache/spark/sql/catalog/Catalog.html) API making use of the [{sparklyr}](https://sparklyr.ai) API. Catalog is the interface for managing a metastore (aka metadata catalog) of relational entities (e.g. database(s), tables, functions, table columns and temporary views).

## Installation

You can install:

* the development version from [GitHub](https://github.com/nathaneastwood/catalog) with

```{r installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("nathaneastwood/catalog")
```

## Usage

{catalog} provides an API matching that of the Catalog API and provides full access to all methods. Below is a small example of some of the functionality.

```{r spark_setup}
sc <- sparklyr::spark_connect(master = "local")
mtcars_spark <- sparklyr::copy_to(dest = sc, df = mtcars)

library(catalog)

list_tables(sc)

list_columns(sc, "mtcars")

list_functions(sc)

drop_temp_view(sc, "mtcars")
```

For more information, please refer to the [package website](https://nathaneastwood.github.io/catalog/).
